### 2025-01-05 README.Rmd
add HistWords to README

* `load_embeddings()` loads pretrained [GloVe](https://nlp.stanford.edu/projects/glove/), [word2vec](https://code.google.com/archive/p/word2vec/), [ConceptNet Numberbatch](https://github.com/commonsense/conceptnet-numberbatch), and [fastText](https://fasttext.cc) word embedding models from Internet sources or from your working directory
* `embed_tokens()` returns the embedding for each token in a set of texts
* `embed_docs()` generates text embeddings for a set of documents
* `get_sims()` calculates row-wise similarity metrics between a set of embeddings and a given reference
* `average_embedding()` calculates the (weighted) average of multiple embeddings
* `reduce_dimensionality()` reduces the dimensionality of embeddings
* `align_embeddings()` rotates the embeddings from one model so that they can be compared with those from another
* `normalize()` and `normalize_rows()` normalize embeddings to the unit hypersphere
* and more...

>>>>

* `load_embeddings()` loads pretrained [GloVe](https://nlp.stanford.edu/projects/glove/), [word2vec](https://code.google.com/archive/p/word2vec/), [HistWords](https://nlp.stanford.edu/projects/histwords/), [ConceptNet Numberbatch](https://github.com/commonsense/conceptnet-numberbatch), and [fastText](https://fasttext.cc) word embedding models from Internet sources or from your working directory
* `embed_tokens()` returns the embedding for each token in a set of texts
* `embed_docs()` generates text embeddings for a set of documents
* `get_sims()` calculates row-wise similarity metrics between a set of embeddings and a given reference
* `average_embedding()` calculates the (weighted) average of multiple embeddings
* `reduce_dimensionality()` reduces the dimensionality of embeddings
* `align_embeddings()` rotates the embeddings from one model so that they can be compared with those from another
* `normalize()` and `normalize_rows()` normalize embeddings to the unit hypersphere
* and more...
